A quantitative analysis of Media Agenda and Public Opinion using time-evolving topic distribution

### 2018-09-11 bmc_article.tex
Algunas minimas correciones

\par Moreover, the methodology implemented here also allowed us to detect coverage bias in newspapers and gave us a first approximation in the theory of framing. The implementation of the word clouds and topic detection algorithms, which were described in this work, allow us to clearly observe the huge differences between any pair of newspapers. In particular, it is shown in figures \ref{fig:news_agenda} and \ref{fig:topics_temporal_profiles}  how \emph{Clarín}, \emph{La Nación} and \emph{Infobae}, that share a similar political view with the current government, focused on the former president \emph{Cristina Fern\'andez de Kirchner}, whereas \emph{P\'agina 12}, the newspaper that  criticizes and condemns the government, focused on the denounced repression that \emph{Santiago Maldonado} suffered from the police.

\par We hope that some of the elements studied here will give us insights at the time of proposing a mathematical model about the interaction between mass media and audience. Future works may include a more systematic study and its extension to international media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality .

@@

\section*{Acknowledgements}
  We thank Dr. A. Chernomoretz, Dr. M. Otero, Dra. V. Semeshenko, and Dr. M. Trevis\'an for bringing us a critical revision of the article.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                  The Bibliography                       %%
%%                                                         %%
%%  Bmc_mathpys.bst  will be used to                       %%
%%  create a .BBL file for submission.                     %%
%%  After submission of the .TEX file,                     %%
%%  you will be prompted to submit your .BBL file.         %%
%%                                                         %%
%%                                                         %%
%%  Note that the displayed Bibliography will not          %%
%%  necessarily be rendered by Latex exactly as specified  %%
%%  in the online Instructions for Authors.                %%
%%                                                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\theendnotes

>>>>

\par Moreover, the methodology implemented here also allowed us to detect coverage bias in newspapers and gave us a first approximation in the theory of framing. The implementation of the word clouds and topic detection algorithms, which were described in this work, allow us to clearly observe the huge differences between any pair of newspapers. In particular, it is shown in figures \ref{fig:news_agenda} and \ref{fig:topics_temporal_profiles}  how \emph{Clar\'in}, \emph{La Naci\'on} and \emph{Infobae}, that share a similar political view with the current government, focused on the former president \emph{Cristina Fern\'andez de Kirchner}, whereas \emph{P\'agina 12}, the newspaper that criticizes and condemns the government, focused on the denounced repression that \emph{Santiago Maldonado} suffered from the police.

\par We hope that some of the elements studied here will give us insights at the time of proposing a mathematical model about the interaction between mass media and audience. Future works may include a more systematic study and its extension to international media, a deeper study of framing through topic detection and sentiment analysis, and a more quantitative analysis about causality.

@@

\section*{Acknowledgements}
  We thank Dr. A. Chernomoretz, Dr. M. Otero, Dra. V. Semeshenko, and Dr. M. Trevis\'an for bringing us a critical revision of the article.

\theendnotes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                  The Bibliography                       %%
%%                                                         %%
%%  Bmc_mathpys.bst  will be used to                       %%
%%  create a .BBL file for submission.                     %%
%%  After submission of the .TEX file,                     %%
%%  you will be prompted to submit your .BBL file.         %%
%%                                                         %%
%%                                                         %%
%%  Note that the displayed Bibliography will not          %%
%%  necessarily be rendered by Latex exactly as specified  %%
%%  in the online Instructions for Authors.                %%
%%                                                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@
